### 2021-04-07 Chapter-3/Chapter-3.tex
Updates from Overleaf

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data and improve performance simultaneously. Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores. The main memory is the bottom-most under the memory hierarchy.
\begin{figure}
  \centering
  \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
\end{figure}

@@

\begin{lstlisting}
 ...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
 ...
\end{lstlisting}

@@

@@

\tool{} works on native x86 execution traces. The design, which is very
precise in terms of true leakages compared to other static source code
method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has
the common limitations of dynamic approaches. \tool{} may only cover part of the code.
Each time we only get one single execution trace. Therefore,
we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
However, this is not a crucial problem for analyzing crypto libraries because crypto
libraries are designed to have the same code coverage for various inputs. Our
evaluation also confirms the above point. For symmetric encryption, during our
evaluation there is no secret-dependent control-flow transfers. RSA
implementations have several secret-dependent control-flow transfers.
%But after we manually check those leakages cites. We find
Most of them are  %used for
bound checks, which do not leak much information and have negligible effects
on the whole code coverage as well.

While recent works have reported lots
of potential side-channel vulnerabilities, most of them are not patched by
developers. For RSA, the latest
OpenSSL only has one leakage site that can leak more than 3 bits while there
are 22 leakage sites according to \tool{}. DES implementation of OpenSSL has
several sensitive leakages, but given the end life status of DES, it is still
unpatched for the worth of engineering effort.

>>>>

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data and improve performance simultaneously. Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores. The main memory is the bottom-most under the memory hierarchy.
\begin{figure}
  \centering
  \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
\end{figure}

@@

\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
 ...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
 ...
\end{lstlisting}

@@

\subsection{Case Studies}
\subsubsection{DES and AES}
Our tool confirms that both implementations in OpenSSL and mbedTLS have side-channel leakages
sites. Moreover, we find that all the leakages belong to the secret-dependent data accesses. The reference implementation of AES uses four lookup tables to speed up the computation. However, such implementation are vulnerable to side-channel attacks. Previous work has shown an end-to-end attack to fully recover the key. Our findings is similar to the previous work. We also notice that later version of OpenSSL (after 1.0.1) uses a modified version with smaller S-table. However, \tool{} also find the leakage sites in the version. Recent work also finds the sites through theoretical analysis.

\subsection{RSA}

@@

\tool{} works on native x86 execution traces. The design, which is very
precise in terms of true leakages compared to other static source code
method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has
the common limitations of dynamic approaches. \tool{} may only cover part of the code.
Each time we only get one single execution trace. Therefore,
we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
However, this is not a crucial problem for analyzing crypto libraries, because crypto
libraries are designed to have the same code coverage for various inputs. Our
evaluation also confirms the above point. For symmetric encryption, during our
evaluation there is no secret-dependent control-flow transfers. RSA
implementations have several secret-dependent control-flow transfers.
%But after we manually check those leakages cites. We find
Most of them are  %used for
bound checks, which do not leak much information and have negligible effects
on the whole code coverage as well.

While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. For RSA, the latest OpenSSL only has one leakage site that can leak more than 3 bits while there are 22 leakage sites according to \tool{}. DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. The sampling method  seems simple and may miss some leakages in theory. However, the evaluation result shows \tool{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.
